Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-09-11 analysis/paper/sim_survey_paper.Rmd
Use new simulation run in paper and tweak figures

devtools::install_github("rstudio/rmarkdown@v1.10")

@@

```{r data, include = FALSE}
library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
library(data.table)
load("analysis/cod_sim_exports/2018-07-13_test/test_output.RData")
```

@@

  p <-  p + 
    geom_ribbon(aes(ymin = lower, ymax = upper, fill = prob, alpha = prob)) +
    geom_line(aes(y = I), data = true, color = viridis::viridis(1), size = 0.7) +
    scale_fill_viridis(name = "Pr", discrete = TRUE, begin = 0.1) +
    scale_alpha_discrete(name = "Pr") + 
    xlab(x) + ylab("Abundance index") +
    scale_y_continuous(labels = format_si()) +
    scale_x_continuous(expand = c(0.01, 0), 
                       labels = xlabs, 
                       breaks = xbreaks) +
    guides(color = guide_legend(keywidth = 0.4, keyheight = 0.25, 
                                default.unit = "cm", ncol = 1))

@@

```{r appen-data}
## this export holds the same distribution test
load("analysis/cod_sim_exports/2018-07-16_test/test_output.RData")
```

>>>>

# devtools::install_github("rstudio/rmarkdown@v1.10")

@@

```{r data, include = FALSE}
library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
library(data.table)
load("analysis/cod_sim_exports/2018-09-04_test/test_output.RData")
```

@@

  p <-  p + 
    geom_ribbon(aes(ymin = lower, ymax = upper, fill = prob, alpha = prob)) +
    geom_line(aes(y = I), data = true, color = "black", size = 0.6) +
    scale_fill_viridis(name = "Pr", discrete = TRUE, begin = 0.1) +
    scale_alpha_discrete(name = "Pr", range = c(0.5, 1)) + 
    xlab(x) + ylab("Abundance index") +
    scale_y_continuous(labels = format_si()) +
    scale_x_continuous(expand = c(0.01, 0), 
                       labels = xlabs, 
                       breaks = xbreaks) +
    guides(color = guide_legend(keywidth = 0.4, keyheight = 0.25, 
                                default.unit = "cm", ncol = 1))

@@

```{r appen-data}
## this export holds the same distribution test
load("analysis/cod_sim_exports/2018-09-07_test/test_output.RData")
```
